On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-03 tt_intro.tex
Def Tunnel
Tunnel is now defined properly.

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (180:1) {$p^\prime$};
            \node[above] at (0:1) {$p^\prime$};

@@

            \foreach \theta in {60,-60,120,-120}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }
          \end{scope}

@@

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (180:1) {$p^\prime$};
            \node[above] at (-60:1) {$p^\prime$};

@@

            \foreach \theta in {0,60,120,-120}{
 	            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }
          \end{scope}

@@

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (180:1) {$p^\prime$};
            \node[above] at (-120:1) {$p^\prime$};

@@

            \foreach \theta in {0,60,-60,120}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }
          \end{scope}

@@

At delay 1, a bead cannot collaborate with its successors in order to stabilize itself. 
In fact, there are just two ways for a bead to get stabilized at delay 1 (or the bead has no place to be stabilized around so that the system halts), as observed in \cite{DHOPRSST2018}. 
One is to be bound and the other is through a 1-in-1-out structure called the tunnel section. 
See Fig.~\ref{fig:TTT_tunnel}. 
A \textit{tunnel section} consists of four beads that occupy four neighbors of one free point. 
In order for an oritatam system to stabilize the bead $w[i]$ at the central point $p$ of a tunnel section, its predecessor $w[i-1]$ must be put at one of the two free neighbors of $p$. 
Thus, at the stabilization of $w[i]$, only one neighbor of $p$ is left free so that the successor $w[i+1]$ is to be stabilized there, even without being bound. 
In this case, the point where $w[i-1]$ is stabilized is considered to be an \textit{entrance of the tunnel section} and the point where $w[i+1]$ is stabilized is considered as its \textit{exit}.

@@

\begin{definition}[Binding Capability]
Let $\alpha$ be an arity and $C = (P,w,H)$ be a conformation of arity at most $\alpha$.
Let $H_k = H \cap \{ (i,j) \mid \mbox{$i=k$ or $j=k$} \}$. 
Moreover, let $R_k$ be a set of neighbors of the point $P[k]$ that are free and reachable from $C$.
The binding capability of $C$ at arity $\alpha$, denoted by $\#bc_\alpha(C)$, is defined by $\sum^{|w|}_{k=1} \min \{\alpha-|H_k|, |R_k|\}$.
The subscript $\alpha$ is omitted whenever it is clear from context. 
\end{definition}

>>>>

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (0,0) {$p_c$};
            \node[above] at (180:1) {$p_e$};
            \node[above] at (0:1) {$p_s$};

@@

            \foreach \theta in {60,-60,120,-120}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }
          \draw[->, blue] (-0.9, 0) -- (-0.1, 0);
          \draw[->, blue] (0.1, 0) -- (0.9, 0);
          \end{scope}

@@

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (0,0) {$p_c$};
            \node[above] at (180:1) {$p_e$};
            \node[right] at (-60:1) {$p_s$};

@@

            \foreach \theta in {0,60,120,-120}{
 	            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }
          \draw[->, blue] (-0.9, 0) -- (-0.1, 0);
          \draw[->, blue] (0,0)++(300:0.1) -- (300:0.8);
          \end{scope}

@@

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (0,0) {$p_c$};
            \node[above] at (180:1) {$p_e$};
            \node[left] at (-120:1) {$p_s$};

@@

            \foreach \theta in {0,60,-60,120}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }
          \draw[->, blue] (-0.9, 0) -- (-0.1, 0);
          \draw[->, blue] (0,0)++(240:0.1) -- (240:0.8);
          \end{scope}

@@

At delay 1, a bead cannot collaborate with its successors in order to stabilize itself. 
In fact, there are just two ways for a bead to get stabilized at delay 1 (or the bead has no place to be stabilized around so that the system halts), as observed in \cite{DHOPRSST2018}. 
One is to be bound to another bead and the other is through a 1-in-1-out structure called the tunnel section. 
See Fig.~\ref{fig:TTT_tunnel}. 
A \textit{tunnel section} consists of one free point $p_c$ and four beads that occupy four neighbors of $p_c$. 
In order for an oritatami system to stabilize the bead $w[i]$ at the central point $p_c$, its predecessor $w[i-1]$ must be put at one of the two free neighbors of $p$. 
Thus, at the stabilization of $w[i]$, only one neighbor of $p$ is left free so that the successor $w[i+1]$ is to be stabilized there, even without being bound. 
In this case, the point $p_e$ where $w[i-1]$ is stabilized is considered to be an \textit{entrance of the tunnel section} and the point $p_s$ where $w[i+1]$ is stabilized is considered as its \textit{exit}. 
A \textit{tunnel} is a maximal set of tunnel sections whose central points form a path.

@@

\begin{definition}[Binding Capability]
Let $\alpha$ be an arity and $C = (P,w,H)$ be a conformation of arity at most $\alpha$.
Let $H_k = H \cap \{ (i,j) \mid \mbox{$i=k$ or $j=k$} \}$. 
Moreover, let $R_k$ be a set of neighbors of the point $P[k]$ that are free and reachable from $C$.
The binding capability of $C$ at arity $\alpha$, denoted by $\#bc_\alpha(C)$, is defined by $\sum^{|w|}_{k=1} \min \{\alpha-|H_k|, |R_k|\}$.
The subscript $\alpha$ is omitted whenever it is clear from context. 
\end{definition}
%
Observe one almost-trivial but important fact that a bead inside a tunnel does not increase the binding capability. 
This is because for such a bead $w[k]$, $|R_k| = 0$.
